Supplement to: Optimal management of a stochastically varying population when policy adjustment is costly

### 2015-06-22 manuscripts/manuscript.Rmd
recompile docs, figures

```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs. When costs vary linearly with the size of the adjustment ($\\Pi_1$), periods with no adjustment are more common than if adjustments were free.  When costs vary quadratically with adjustment size ($\\Pi_2$), small adjustments are relatively cheap and thus the resulting optimal policy always changes, but by a smaller amount than if adjustments were free.  When adjustments incur a fixed fee independent of size ($\\Pi_3$), the optimal strategy either remains unchanged or overshoots the cost-free optimum. ", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}

@@

ggplot(dt3, aes(time, value, col=variable, lty=variable)) +
  geom_line(lwd=1) +
  facet_grid(penalty_fn~., labeller = labeller) + 
  labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
  scale_color_discrete(labels=c("Adjustment penalty", "No penalty"), name="") +
  scale_linetype_discrete(labels=c("Adjustment penalty", "No penalty"), name="") + 
  theme_bw()

@@

In the supplemental material, Figures S9-S12 illustrate that the 
these qualitative patterns still hold at when the models are calibrated 
to a reduction in NPV of 10% or 30%, though naturally the magnitude
of the pattern is greater when the penalty is larger (e.g. 30% vs 10%).

@@

```{r Figure_6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.  All values are relative to the cost free adjustment optimum, $NPV_0$.  In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present. The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}

>>>>

```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy under the different functional forms of adjustment costs. When costs vary linearly with the size of the adjustment ($\\Pi_1$), periods with no adjustment are more common than if adjustments were free.  When costs vary quadratically with adjustment size ($\\Pi_2$), small adjustments are relatively cheap and thus the resulting optimal policy always changes, but by a smaller amount than if adjustments were free.  When adjustments incur a fixed fee independent of size ($\\Pi_3$), the optimal strategy either remains unchanged or overshoots the cost-free optimum. ", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}

@@

ggplot(dt3, aes(time, value, col=variable, lty=variable)) +
  geom_line(lwd=1) +
  facet_grid(penalty_fn~., labeller = labeller) + 
  labs(x="time", y="harvest", title = "Example Harvest Dynamics")  +
  scale_color_discrete(labels=c("Adjustment penalty", "No penalty"), name="") +
  scale_linetype_discrete(labels=c("Adjustment penalty", "No penalty"), name="") + 
  theme_bw()

@@

Figure 4 shows these qualitative patterns still hold at when the models are calibrated 
to a range of different reductions in NPV, from 0% to 30%, though naturally the magnitude
of the differences is greatest when the penalty is larger.

@@

```{r Figure_6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue).  All values are relative to the cost free adjustment optimum, $NPV_0$.  In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.Supplementary Figure S6 shows how the magnitude of this effect changes with the size of the reduction to $NPV$.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}

### 2015-06-22 manuscripts/supplement.Rmd
update figures
recompile docs, figures

\renewcommand{\thefigure}{S\arabic{figure}}
\appendix

@@

```{r Figure_S1, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}

@@

```{r}
source("components/vary_reduction.R")
```

>>>>

\appendix
\renewcommand\thefigure{S\arabic{figure}}

@@

```{r Figure_S1, dependson="tidy", fig.cap="Example realization of optimal fish stock sizes under the different functional forms of adjustment costs, under the harvest policy dynamics shown in Figure 3 of the main text.", fig.height=5, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}

@@

```{r}
parallel = TRUE
ncpu = parallel::detectCores()
price = 10
c0 = 30
profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
#c2 <- exp(seq(0, log(41), length.out = 40))-1
c2 <- seq(0, 40, length.out=100)
reduction <- 0.25 
seed <- 123                 # Random seed (replicable results)
delta <- 0.05               # economic discounting rate
OptTime <- 50               # stopping time
gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
sigma_g <- 0.2              # Noise in population growth
reward <- 0                 # bonus for satisfying the boundary condition
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1         # No measurement noise, 
z_i <- function() 1         # No implemenation noise
f <- BevHolt                # Select the state equation
pars <- c(1.5, 0.05)        # parameters for the state equation
K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
xT <- 0                     # boundary conditions
x0 <- K
x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- seq(0.01, 0.8 * K, length = gridsize)

source("components/vary_reduction.R")
```

<!--
